Specifying BYOD Policies with Authorization Logic

### 2016-03-09 paper.tex
UNFINISHED: moved bibtex inline since it is so short and made space

\title{Specifying BYOD Policies With Logics Of Authorization}
\titlerunning{Specifying BYOD Policies With Logics Of Authorization}
\author{
  Joseph Hallett\inst{1}
  \and
  David Aspinall\inst{1}
}
\authorrunning{Hallett and Aspinall}

@@

@@

\begin{abstract}
  % State problem
  % Why is it interesting
  % What does my solution achieve
  % What follows from solution
\end{abstract}

@@

Employees are increasingly bringing their own devices into their workplaces (called \emph{bring your own device} or BYOD schemes).
This can present a challenge for corporate IT departments:
  they need to secure their networks and data but as they do not provide the employees with the devices they have limited control over what software runs and how the devices are configured.
As a means of controlling the devices, IT departments have taken to publishing mobile device policies.
Employees must agree to follow these policies if they want to use their personal devices in work.
Often these policies are specified using natural language.
This is problematic as it can create ambiguity in how the policy should be enforced, and in how the IT department can confirm that the policy was followed.
There may be issues with \emph{completeness} and \emph{consistency} in these policies, which can lead to problems in enforcement.

@@

\section{Translating Corporate Policies}
\label{sec:translation}

@@

Some rules also appear to be common between different policies.
For example both the NHS and SANS policies contain rules on the use of mobile devices in cars.
The NHS policy requires employees do not use devices in cars, and recommends against using them even with hands-free equipment:
\begin{lstlisting}[title={\footnotesize\textbf{NHS}:~\itshape ``%
For safety reasons, Trust staff must not use a hand held mobile device whilst driving any vehicle. It is illegal to do so. Please refer to the most up-to-date information via the Highways Agency.  For safety reasons, Trust staff must not use a hand held mobile device whilst driving any vehicle. It is illegal to do so. Please refer to the most up-to-date information via the Highways Agency.''}]
'nhs-policy' says Device mustNotOperate 
  if Device isOwnedBy(Owner)
  where inCar(Device) = true, isDriving(Owner) = true.
\end{lstlisting}
Whereas the SANS policy requires the use of hands-free devices when in a car.
\begin{lstlisting}[title={\footnotesize\textbf{SANS}:~\itshape ``Conducting telephone calls or utilizing handhelds while driving can be a safety hazard. Drivers should use handhelds in hand only while parked or out of the vehicle.
If employees must use a handheld device while driving, ⟨Company⟩ requires the use of hands-free headset devices.''}]
'sans-policy' says Device mustNotOperate 
  if Device isOwnedBy(Owner)
  where inCar(Device) = true, isDriving(Owner) = true, isUsingHandsFree(Device) = false.
\end{lstlisting}
The similarity between the two rules is immediately apparent when specified in AppPAL: the SANS version has an additional constraint but they are otherwise identical.
Other similarities appear when looking at how devices connect to networks.  The Edinburgh policy recommends disabling automatic access to open unsecured Wi-Fi networks:
\begin{lstlisting}[title={\footnotesize\textbf{Edinburgh}:~\itshape ``Control your devices connections by disabling automatic connection to open, unsecured Wi-Fi networks''}]
'edinburgh-policy' says Device canConnectTo(AP) if AP isSecure.
\end{lstlisting}

Similarities between policies suggest that one could define a common schema of BYOD predicates, which would allow different policies to be compared and contrasted \emph{precisely} using standard terms.

@@

\bibliographystyle{plain}
\bibliography{paper}
\end{document}

>>>>

\title{Specifying BYOD Policies with Authorization Logic}
\titlerunning{Specifying BYOD Policies with Authorization Logic}
\author{
  Joseph Hallett\inst{1}
  \and
  David Aspinall\inst{1}
}
\authorrunning{Hallett and Aspinall}

@@

\newcommand{\dotdotdot}[1]{$\[\cdots\]$}

@@

\begin{abstract}
  % State problem
  Corporate BYOD policies are imprecisely specified using natural language.
  % Why is it interesting
  This creates ambiguity and makes detecting issues, and comparing policies harder.
  % What does my solution achieve
  We show how AppPAL (an authorization logic for mobile app installation policies) can describe BYOD policies formally.
  % What follows from solution
  This suggests that BYOD policies can be enforced automatically, and with greater precision, than by relying on users.
\end{abstract}

@@

Employees are increasingly bringing their own devices into their workplaces.
This can present a challenge for corporate IT departments:
  they need to secure their networks and data but as they do not provide the employees with the devices they have limited control over what software runs and how the devices are configured.
As a means of controlling the devices, IT departments have taken to publishing mobile device policies.
Employees must agree to follow these policies if they want to use their personal devices in work.
Often these policies are specified using natural language.
This is problematic as it can create ambiguity in how the policy should be enforced, and in how the IT department can confirm that the policy was followed.
There may be issues with \emph{completeness} and \emph{consistency} in these policies, which can lead to problems in enforcement.

@@

\section{Translating Corporate BYOD Policies}
\label{sec:translation}

@@

Some rules also appear to be common between different policies.
For example both the NHS and SANS policies contain rules on the use of mobile devices in cars.
The NHS policy requires employees do not use devices in cars, and recommends against using them even with hands-free equipment:
\begin{lstlisting}[title={\footnotesize\textbf{NHS}:~\itshape ``%
For safety reasons, Trust staff must not use a hand held mobile device whilst driving any vehicle. It is illegal to do so. Please refer to the most up-to-date information via the Highways Agency.  For safety reasons, Trust staff must not use a hand held mobile device whilst driving any vehicle. It is illegal to do so. Please refer to the most up-to-date information via the Highways Agency.''}]
'nhs-policy' says Device mustNotOperate 
  if Device isOwnedBy(Owner)
  where inCar(Device) = true, isDriving(Owner) = true.
\end{lstlisting}
Whereas the SANS policy requires the use of hands-free devices when in a car.
\begin{lstlisting}[title={\footnotesize\textbf{SANS}:~\itshape ``Conducting telephone calls or utilizing handhelds while driving can be a safety hazard. Drivers should use handhelds in hand only while parked or out of the vehicle.
If employees must use a handheld device while driving, ⟨Company⟩ requires the use of hands-free headset devices.''}]
'sans-policy' says Device mustNotOperate 
  if Device isOwnedBy(Owner)
  where inCar(Device) = true, isDriving(Owner) = true, isUsingHandsFree(Device) = false.
\end{lstlisting}
The similarity between the two rules is immediately apparent when specified in AppPAL: the SANS version has an additional constraint but they are otherwise identical.
Other similarities appear when looking at how devices connect to networks.  The Edinburgh policy recommends disabling automatic access to open unsecured Wi-Fi networks, where as SANS says its okay if the access point is secured properly or a VPN is used:
\begin{lstlisting}[title={\footnotesize\textbf{Edinburgh}:~\itshape ``Control your devices connections by disabling automatic connection to open, unsecured Wi-Fi networks.''}]
'edinburgh-policy' says Device canConnectTo(AP) if AP isSecure.
\end{lstlisting}
\begin{lstlisting}[title={\footnotesize\textbf{SANS}:~\itshape ``If mobile workers do require connectivity through public, open, or untrusted WLAN, then users MUST use WLANs using, if available and in this order: WPA(2) encryption, WEP 256 bits (or 128 bits), or finally open networks if nothing else is available. Users connected to data networks in an open environment MUST use a VPN connection.''}]
'sans-policy' says Device canConnectTo(AP) if AP isSecure.
'sans-policy' says AP isSecure if AP canUseWPA2.
'sans-policy' says AP isSecure if AP canUseWEP256.
'sans-policy' says AP isSecure if AP canUseWEP128.
'sans-policy' says Device canConnectTo(AP) if Device hasVPN(VPN) where connect(VPN) = true.
\end{lstlisting}
Similarities between policies suggest that one could define a common schema of BYOD predicates, which would allow different policies to be compared \emph{precisely} using standard terms.

@@

We have shown...

\bibliographystyle{plain}
\begin{thebibliography}{1}
\bibitem{Becker:2006vh}
M.Y. Becker, C~Fournet, and A~D Gordon.
\newblock {SecPAL: Design and semantics of a decentralized authorization language}.
\newblock {\em Computer Security Foundations}, 2006.

\bibitem{Guerin:2008we}
N.R.C. Gu{\'e}rin.
\newblock {Security Policy for the use of handheld devices in corporate environments},
\newblock {\em SANS}.%, 2008.

\bibitem{Hallett:2016vu}
J. Hallett and D. Aspinall.
\newblock {AppPAL for Android}.
\newblock {\em Engineeering Secure Software and Systems}, 2016.

\bibitem{Kennington:2014tr}
G. Kennington, et~al.
\newblock {Mobile Devices Policy},
\newblock {\em Torbay and Southern Devon Health Care NHS Trust}.%, 2014.

\bibitem{Williamson:2015tr}
D. Williamson, A. Grzybowski, and S. Graham.
\newblock {BYOD Policy: Use of Personally Owned Devices for University Work},
\newblock {\em University of Edinburgh}.%, 2015.
\end{thebibliography}
\end{document}
